% % Abstract

\thispagestyle{empty}
\pdfbookmark[0]{Abstract}{Abstract} % Bookmark name visible in a PDF viewer

\begin{center}
%	\bigskip

    {\normalsize \href{http://www.sussex.ac.uk/}{\myUni} \\} % University name in capitals
    {\normalsize \myFaculty \\} % Faculty name
    {\normalsize \myDepartment \\} % Department name
    \bigskip\vspace*{.02\textheight}
    {\Large \textsc{Doctoral Thesis}}\par
    \bigskip
    
    {\rule{\linewidth}{1pt}\\%[0.4cm]
    \Large \myTitle \\
    \large  \mySubtitle \par} % Thesis title
    \rule{\linewidth}{1pt}\\[0.4cm]
    
    \bigskip
	{\normalsize by \myName \par} % Author name
    \bigskip\vspace*{.06\textheight}
\end{center}

    {\centering\Huge\textsc{\textbf{Abstract}} \par}
    \bigskip



    \noindent In this thesis I present all the work that I have done during my PhD. First, I will present the search for the supersymmetric partner of the \ltau\ in 13 \tev\ proton-proton collisions at the LHC using data collected between 2015 and 2018 by the ATLAS detector, for events characterised by two hadronically decaying \ltau s
    and missing transverse momentum in the final states. In this analysis I have been responsible for the signal region optimisation, the optimisation of the triggers and the theory systematic calculation. Results were interpreted considering natural supersymmetric extensions to the standard model in the $R$-parity conserving decays. No significant excess was observed and stringent exclusion limits were set. 
    During my PhD I have also had leading involvement in the characterisation of the performances of the Inner Detector Trigger, which I will discuss in this thesis. 
Finally, stemming from my analysis work, I had major involvement in the study of a novel technique for estimating the contribution of mis-identified \ltau s in signal enriched regions. A tool using this technique is currently under development in the ATLAS collaboration, that will become ATLAS approved in the very near future. 
    
    %of the top quark in $\sqrt{s}=13$ \TeV\ proton-proton collisions at the LHC using data collected by the ATLAS detector in 2015 and 2016. Results were interpreted considering natural supersymmetric extensions of the Standard Model in $R$-parity conserving decays. Events characterised by four or more jets and missing transverse momentum in the final states were selected. The performance of the tracking algorithms used by the ATLAS online trigger were studied. Optimisation studies of the search regions to increase the sensitivity to supersymmetric signals were performed and data-driven techniques to estimate Standard Model backgrounds were employed. The agreement between data and background predictions was extensively checked and the extrapolations from background-enriched regions to signal-enriched regions were validated. The analysis yielded no significant excess therefore exclusion limits on various models were set.


